DataCamp: An Interactive Teaching Tool

### 2018-01-06 manuscript.tex
added manuscript pdf - need help with figures
edit manuscript

The goal for any statistics course is to help students develop the ability to think statistically
\citep{AmericanStatisticalAssociation2016}; introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive computational abilities (free of charge) and are commonly used in statistics courses. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

@@

\subsubsection{Try R}
Try R \citep{TryR} is another interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
The R console can be intimidating to
new statistics students so an advantage of web-based teaching tools is
the clean and easy to use interface. User-friendliness is an important quality given that students often struggle more with the
software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the lesson.
However, Try R is not open source so public content authoring
is not available; educators are limited to the existing lessons available on the Try R website.

\section{DataCamp}

@@

\subsubsection{DataCamp compared to similar technologies}
DataCamp provides the same reproducible capabilities as \textit{swirl} but is a web-based application. Educators can
create their own courses that coincide with specific lessons and students can access the course without installing any software.
Courses are available through the DataCamp website so students can access the lesson through their web-browser on a laptop,
tablet or mobile device, making the courses accessible to anyone with an internet connection. These programming courses can be used in the 
classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
for a flipped classroom, and even as a test or assessment tool.

@@

\subsubsection{Gamification}
Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
progress (points and chapters completed) as well as the progress of their peers. This can help students perform better
in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution.

@@

\begin{figure}[h]
  \includegraphics[scale = 0.20] {preview.jpg}
\end{figure}
\subsubsection{Exercise Header}
Whenever a new exercise is added, DataCamp automatically produces the top line of the editor. The header specifies the type
of exercise (\texttt{type}), programming language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills}) and a \texttt{key}. 
The types of exercises include normal coding, video, and multiple choice exercises; we will discuss these further in the next section. In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
DataCamp assigns 100 points \texttt{xp} to normal coding exercises but this value can be modified depending on
difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
The \texttt{skills} portion of the header refers to DataCamp's
eight different skill sets, defined by numbers 1-8. Skills and their corresponding numbers can be found in the DataCamp
documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
Lastly, the \texttt{key} acts as a unique
identifier for that exercise, allowing you to modify content without losing any student data. 
In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
corresponds to R Programming).

@@

Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
Instructors write the questions in the lesson
portion of the exercise and offer solutions in the \texit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
\begin{figure}
\caption{This code does this}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1
    key:9707072219

>>>>

The goal of any statistics course is to help students develop the ability to think statistically
\citep{AmericanStatisticalAssociation2016}; introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive computational abilities (free of charge) and are commonly used in statistics courses. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

@@

\subsubsection{Try R}
Try R \citep{TryR} is another interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
The R console can be intimidating to
new statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. User-friendliness is an important quality given that students often struggle more with the
software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the lesson.
However, Try R is not open source so public content authoring
is not available; educators are limited to the existing lessons available on the Try R website.

\section{Introduction to DataCamp}

@@

DataCamp provides the same reproducible capabilities as \textit{swirl} but is a web-based application. Educators can
create their own courses that coincide with specific lessons and students can access the course without installing any software.
Courses are available through the DataCamp website so students can access the lesson through their web-browser on a laptop,
tablet or mobile device, making the courses accessible to anyone with an internet connection. These programming courses can be used in the 
classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
for a flipped classroom, and even as a test or assessment tool.

@@

\subsubsection{Gamification}
Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
progress (points and chapters completed) as well as the progress of their peers. Students will often perform better
in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
of the available points are deducted; all points are deducted if they ask for the solution.

@@

\begin{figure}[h]
  \includegraphics[scale = 0.40] {preview.jpg}
\end{figure}
\subsubsection{Exercise Header}
Whenever a new exercise is added, DataCamp automatically produces the top line of the editor. The header specifies the type
of exercise (\texttt{type}), programming language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills}) and a \texttt{key}. 
The types of exercises include normal coding, video, and multiple choice exercises; we will discuss these further in the next section. In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
DataCamp assigns 100 points \texttt{xp} to normal coding exercises but this value can be modified depending on
difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
The \texttt{skills} portion of the header refers to DataCamp's
eight different skill sets, defined by numbers 1-8. Skills and their corresponding numbers can be found in the DataCamp
documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
Lastly, the \texttt{key} acts as a unique
identifier for that exercise, allowing you to modify content without losing any student data. 
In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
corresponds to R Programming).

@@

Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
Instructors write the questions in the lesson
portion of the exercise and offer solutions in the \textit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
\begin{figure}
\caption{This should be in section 3.4.3}
\begin{Verbatim}[frame=single]
--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1
    key:9707072219
